\chapter{Summary}

The inversion of a neural network has not received much attention since the rise of machine learning, and Python's machine learning libraries have not encompassed any inversion methods. In this paper a solution was given for computing the inversion of a function approximated by neural networks. \medskip

Three main tasks were tackled in this paper to perform a solution: data mining for extracting information from the data set, building and testing multi-layer perceptron models, and the inversion of the single element feedforward neural network. The presented tasks were performed in Python with the assistance of its third-party libraries. \medskip

The goal is to perform the inversion, for what a sufficient number of neural network models has to be established. The necessary tasks are described in the thesis. Data mining was used for extracting information from the data set. Multi-layer perceptron models were built and tested with numerous hyperparameter combinations to find the best fitting combination which can predict the outputs the best. Then the single element inversion of the feedforward neural network was completed by the Williams-Linder-Kindermann inversion. \medskip

The Online News Popularity dataset, which is a publicly available dataset was used during the whole process from data mining to the inversion. Various data mining and cleaning techniques were proceeded on the dataset to make it ready for training. After the optimization, the training was running in parallel on the supercomputer with thousands of hyperparameter combinations of the multi-layer perceptron. After thousands of iterations the neural network mean test score has not reached acceptable levels yet. WLK inversion has been tested on smaller datasets with trained neural network with good results. \medskip

For further plans, the best fitting parameter combination has to be found in respect for the processed dataset. To achieve it, the dataset needs more data cleaning steps and to think over to get more features with predictable information. Also, expanding the amount of hidden layers can increase the accuracy of the fitting. \medskip

This paper contains applied machine learning research in the field of artificial intelligence with the implementation of neural network inversion. Furthermore as a future plan, this explanation will be sent to Scikit-Learn as a scientific solution of the inversion problem. 